### 2022-01-19 sections/signal_background_modeling.tex
solve the commets

>>>>

\begin{table}
\footnotesize
\centering
\caption{Overview of the MC generators used for the main signal and background samples}
\begin{tabular}[h]{l|c|c|c|c|c|c}
\hline \hline
\multirow{2}{*}{Process} & \multicolumn{2}{c|}{Generator} & \multicolumn{2}{c|}{PDF set} & \multirow{2}{*}{Tune} & \multirow{2}{*}{Order} \\ \cline{2-5}
        &  ME   &  PS    &  ME  & PS &   &  \\\hline
\textit{TT} Signal & Powheg & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
\textit{ST} Signal & MadGraph5\_aMC@NLO & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
$W/Z$+jets & \multicolumn{2}{c|}{Sherpa 2.2.1} & \multicolumn{2}{c|}{NNPDF30NNLO} & Sherpa & NLO/LO \\ \hline
\ttbar & Powheg & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
Single top & Powheg & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
$t\bar{t}X$ & MadGraph5\_aMC@NLO & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
Diboson & \multicolumn{2}{c|}{Sherpa 2.2.1} & \multicolumn{2}{c|}{NNPDF30NNLO} & Sherpa & NLO/LO \\ \hline\hline
\end{tabular}
\label{mob}
\end{table}

### 2022-01-19 sections/strategy_Htautau.tex
solve the commets

%%%%%%%%%%%%%%%
\begin{table*}[t!]
\caption{\small{$\Htautau$ search: Discriminating variables used in the training of the BDT for leptonic channel.
    The description of each variable is provided in the text.}}
\label{tab:importance_tthML}
\input{\FCNCTables/Importance/tthML/Merged}
\end{table*}

\begin{table*}[t!]
\caption{\small{$\Htautau$ search: Discriminating variables used in the training of the BDT for hadronic channel. 
    The description of each variable is provided in the text.}}
\label{tab:importance_xTFW}
\input{\FCNCTables/Importance/xTFW/Merged}
\end{table*}

%%%%%%%%%%%%%%%

@@

A large set of potential variables are investigated in each SR separately. The discrimination of a given variable is quantified by the ``separation" and ``importance" measures provided by the TMVA package~\cite{Hocker:2007ht}, and only those variables whose importance is large than 2\% were kept.

@@

\item $E^{T}_{miss}$ is the missing transverse momentum.
\item $p_{T,\tau}$ is the transverse momentum of the leading tau candidate.
\item $p_{T,sub-\tau}$ is the transverse momentum of the sub-leading tau candidate.
\item $p_{T,l}$ is the transverse momentum of the leading lepton.

@@

\item $m_{t,SM}$ is the invariant mass of the $b$-jet and the two jets from the $W$ decay, and reflects the top mass in the decay $t\to Wb \to j_1j_2b$. This variable is only defined for the 4-jet $t_hH$ and $t_ht(qH)$ events.
\item $m^{T}_{W}$ is the transverse mass calculated from the lepton and $\met$ in the leptonic channels, defined as

@@

m^{T}_{W} = \sqrt{2 p_{\text{T,lep}} E_{\text{T}}^{\text{miss}} \left(1-\cos\Delta\phi_{\text{lep,miss}} \right)}.  

@@

\item $m_{W}$ is the reconstructed invariant mass of the hadronic $W$ boson from SM top quark.
\item $m_{t,FCNC}$ is the fitted invariant mass of the FCNC-decaying top quark reconstructed from di-tau candidates, $q$-jet and reconstructed neutrinos.
\item $m_{\tau\tau,vis}$ is the visible invariant mass of the di-tau candidates.
  %or the lepton and $\had$ candidate when there is only one $\had$.
\item $p_{T,\tau\tau,vis}$ is the $\pt$ of the di-tau candidates.
\item $m_{t,FCNC,vis}$ is the reconstructed visible mass of the FCNC-decaying top quark.
\item $m_{t,SM,vis}$ is the invariant mass of the lepton and the b-jet, which reflects the visible SM top mass.
\item $M(\tau\tau qjet,min)$ is the visible mass of the di-tau candidates (include leptonic tau) and the light-flavor jet, minimized by choosing different jet, reflects the invariant mass of the visible FCNC top decaying product, an alternative of variable $m_{t,FCNC,vis}$.
\item $M(wjet1,wjet2,min)$ is the invariant mass of two light-flavor jet, minimized by choosing different jets, reflects the invariant mass of the W candidate, an alternative of $m_{W}$.

@@

\item $E_{\nu,i}/E_{\tau,i},i=1,2$ is the momentum fraction carried by the visible decay products from the tau mother. It is based on the best-fit 4-momentum of the neutrino(s) according to the event reconstruction algorithm in this section. For the $\tauhad$ decay mode, the visible decay products carry most of the tau energy since there is only a single neutrino in the final state.% which is evident in the excess around 1 in Figure \ref{fig:x12_fit}. 
\item $\Delta R(l+bjet,\tau\tau)$ is the angular distance between the lepton+b-jet and di-tau candidates.
\item $\Delta R(l,bjet)$ is the angular distance between the lepton and b-jet.
\item $\Delta R(\tau,bjet)$ is the angular distance between the tau and b-jet. If there are two taus in the event, the leading one is selected for the calculation.
\item $\eta_{\tau,max}$ is the maximum $\eta$ value among the tau candidates.
\item $\Delta R(l,\tau)$ is the angular distance between the lepton and the closest tau candidate in the leptonic channels.
\item $\Delta R(\tau,qjet)$ is the angular distance between the tau and the reconstructed $q$-jet. If there are two taus in the event, the leading one is used.
\item $\Delta R(\tau,\tau)$ is the angular distance between two tau candidates, in case of $t_h\tlhad$ channels, the definition is the same as $\Delta R(l,\tau)$.
\item $\Delta\phi(\tau\tau,P^{T}_{miss})$ is the azimuthal angle between the $\met$ and di-tau $\pt$.

@@

is shown in Figures~\ref{fig:taupt_postfit}.

@@

The expected signals (dashed) are also shown after scaled up for the shape comparison of the distributions.

@@

The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction.

@@

The final observable used to extract signal events is defined as the BDT distribution in each SRs corresponding to either $tuH$ or $tcH$ signal.
Figure~\ref{fig:asimov_prefitbdt} show the prefits to the data of BDT observable in each SRs with all background processes
constrained to the SM expectation.
%The level of discrimination between signal and background achieved by the BDTs is illustrated in Figure~\ref{fig:overtrain_hadhad}-~\ref{fig:overtrain_lhadhad}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\input{\FCNCFigures/tex/BDTinput}
\begin{figure}[H]
\centering
\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l2tau1bnj_os/tau_pt_0.pdf}
\put(-40, 90){\small\textbf{(a1)}}
%\put(-30, 80){\textbf{(a1)}}
\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b1j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}
\put(-40, 90){\small\textbf{(a2)}}
%\put(-30, 80){\textbf{(a2)}}
\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}
\put(-40, 90){\small\textbf{(a3)}} 
%\put(-70, 70){\textbf{(a3)}}
\\
\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_os_vetobtagwp70_highmet/tau_pt_0.pdf}
\put(-40, 90){\small\textbf{(b1)}}
\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b3j_os_vetobtagwp70_highmet/tau_pt_0.pdf}
\put(-40, 90){\small\textbf{(b2)}}\\
\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/xTFW/showFake/NOMINAL/reg2mtau1b2jos_vetobtagwp70_highmet/tau_pt_0.pdf}
\put(-40, 90){\small\textbf{(c1)}}
\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/xTFW/showFake/NOMINAL/reg2mtau1b3jos_vetobtagwp70_highmet/tau_pt_0.pdf}
\put(-40, 90){\small\textbf{(c2)}}\\
\caption{The leading $\thad$ $p_T$  distributions are compared between the expected background and $tqH$ signals in: $t_l\thadhad$ (a1),  $t_l\tauhad$-1j (a2),  $t_l\tauhad$-2j (a3),
  $t_h\tlhad$-2j (b1), $t_h\tlhad$-3j (b2), $t_h\thadhad$-2j (c1), and $t_h\thadhad$-3j (c2). Only statistical uncertainties are being shown (?). Underflow and overflow bins are included
respectively in the first and last bins. Empty data bins here are always blinded based on our strategy. The real tau
contributions shown from $t\bar{t}$, Ztautau and other MC including diboson, single top, and V+jets.}
\label{fig:taupt_postfit}
\end{figure}

%\input{\FCNCFigures/tex/BDT}
\begin{figure}[H]
\centering
\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l2tau1bnj_os/BDTG_test.pdf}
\put(-40, 90){\small\textbf{(a1)}}
\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b1j_ss_vetobtagwp70_highmet/BDTG_test.pdf}
\put(-40, 90){\small\textbf{(a2)}}
\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_ss_vetobtagwp70_highmet/BDTG_test.pdf}
\put(-40, 90){\small\textbf{(a3)}}\\
\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_os_vetobtagwp70_highmet/BDTG_test.pdf}
\put(-40, 90){\small\textbf{(b1)}}
\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b3j_os_vetobtagwp70_highmet/BDTG_test.pdf}
\put(-40, 90){\small\textbf{(b2)}}\\
\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/xTFW/showFake/NOMINAL/reg2mtau1b2jos_vetobtagwp70_highmet/BDTG_test.pdf}
\put(-40, 90){\small\textbf{(c1)}}
\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/xTFW/showFake/NOMINAL/reg2mtau1b3jos_vetobtagwp70_highmet/BDTG_test.pdf}
\put(-40, 90){\small\textbf{(c2)}}\\
\caption{ The BDT output distributions are compared between the expected background and $tqH$ signals in: $t_l\thadhad$ (a1),  $t_l\tauhad$-1j (a2),  $t_l\tauhad$-2j (a3),
  $t_h\tlhad$-2j (b1), $t_h\tlhad$-3j (b2), $t_h\thadhad$-2j (c1), and $t_h\thadhad$-3j (c2). Only statistical uncertainties are being shown (?). Underflow and overflow bins are included
respectively in the first and last bins. Empty data bins here are always blinded based on our strategy. The real tau
contributions shown from $t\bar{t}$ and other MC including diboson, single top, and V+jets.}
\label{fig:asimov_prefitbdt}
\end{figure}

>>>>

%%%%%%%%%%%%%%%
\begin{table*}[t!]
\caption{\small{$\Htautau$ search: Discriminating variables used in the training of the BDT for hadronic channel. 
    The descriptions of each variable are provided in the following text.}}
\label{tab:importance_xTFW}
\input{tables/xTFW_Merged}
\end{table*}

\begin{table*}[t!]
\caption{\small{$\Htautau$ search: Discriminating variables used in the training of the BDT for leptonic channel. 
    The descriptions of each variable are provided in the following text.}}
\label{tab:importance_tthML}
\input{tables/tthML_Merged}
\end{table*}

@@

A large set of potential variables are investigated in each SR separately. The discrimination of a given variable is quantified by the "separation"(measures the degree of overlap between background and signal shape) and "importance"(depicts the power of the variable to the classification of two distributions) provided by the TMVA package~\cite{Hocker:2007ht}, and only those variables whose importance is large than 2\% were kept.

@@

\item $\MET$ is the missing transverse momentum.
\item $P_{\text{T,\tauhadvis}} $ is the transverse momentum of the leading tau candidate.
\item $P_{\text{T,sub}-\tau}$ is the transverse momentum of the sub-leading tau candidate.
\item $P_{\text{T},\ell}$ is the transverse momentum of the leading lepton.

@@

\item $m_{t,\text{SM}}$ is the invariant mass of the $b$-jet and the two jets from the $W$ decay, and reflects the top mass in the decay $t\to Wb \to j_1j_2b$. This variable is only defined for the 4-jet $t_hH$ and $t_ht(qH)$ events.
\item $m^{T}_{\text{W}}$ is the transverse mass calculated from the lepton and $\met$ in the leptonic channels, defined as

@@

m^{T}_{\text{W}} = \sqrt{2 P_{T,\ell} E_{\text{T}}^{\text{miss}} \left(1-\cos\Delta\phi_{\ell,\text{miss}} \right)}.  

@@

\item $m_{\text{W}}$ is the reconstructed invariant mass of the hadronic $W$ boson from SM top quark.
\item $m_{\text{t},\text{FCNC}}$ is the fitted invariant mass of the FCNC-decaying top quark reconstructed from di-tau candidates, $q$-jet and reconstructed neutrinos.
\item $m_{\tau\tau,\text{vis}}$ is the visible invariant mass of the di-tau candidates. %or the lepton and $\had$ candidate when there is only one $\had$.
\item $P_{\text{T},\tau\tau,\text{vis}}$ is the $\pT$ of the di-tau candidates.
\item $m_{\text{t},\text{SM},\text{vis}}$ is the reconstructed visible mass of the FCNC-decaying top quark.
\item $m_{\text{t},\text{SM},\text{vis}}$ is the invariant mass of the lepton and the b-jet, which reflects the visible SM top mass.
\item $M(\tau\tau \text{qjet},\text{min})$ is the visible mass of the di-tau candidates (include leptonic tau) and the light-flavor jet, minimized by choosing different jet, reflects the invariant masss of the visible FCNC top decaying product, an alternative of variable $m_{\text{t},\text{FCNC},\text{vis}}$.
\item $M(\text{wjet1},\text{wjet2},\text{min})$ is the invariant mass of two light-flavor jet, minimized by choosing different jets, reflects the invariant mass of the W candidate, an alternative of $m_{\text{W}}$.

@@

\item $E_{\nu,\text{i}}/E_{\tau,\text{i}},\text{i}=1,2$ is the momentum fraction carried by the visible decay products from the tau mother. It is based on the best-fit 4-momentum of the neutrino(s) according to the event reconstruction algorithm in this section. For the $\tauhad$ decay mode, the visible decay products carry most of the tau energy since there is only a single neutrino in the final state.% which is evident in the excess around 1 in Figure \ref{fig:x12_fit}. 
\item $\Delta R(\ell+\text{bjet},\tau\tau)$ is the angular distance between the lepton+b-jet and di-tau candidates.
\item $\Delta R(\ell,\text{bjet})$ is the angular distance between the lepton and b-jet.
\item $\Delta R(\tau,\text{bjet})$ is the angular distance between the tau and b-jet. If there are two taus in the event, the leading one is selected for the calculation.
\item $\eta_{\tau,\text{max}}$ is the maximum $\eta$ value among the tau candidates.
\item $\Delta R(\ell,\tau)$ is the angular distance between the lepton and the closest tau candidate in the leptonic channels.
\item $\Delta R(\tau,\text{qjet})$ is the angular distance between the tau and the reconstructed $q$-jet. If there are two taus in the event, the leading one is used.
\item $\Delta R(\tau,\tau)$ is the angular distance between two tau candidates, in case of $t_h\tlhad$ channels, the definition is the same as $\Delta R(\ell,\tau)$.
\item $\Delta\phi(\tau\tau,P^{T}_{\text{miss}})$ is the azimuthal angle between the $\met$ and di-tau $\pT$.

@@

is shown in Figures~\ref{fig:taupt_prefit}.

@@

The expected signals are also shown after scaled up for the shape comparison of the distributions.

@@

The bottom panel displays the ratio of data to the background (``Bkg'') prediction.

@@

The final observable used to extract signal events is defined as the BDT distribution in each SRs corresponding to either $tuH$ or $tcH$ signal.
%Figure~\ref{fig:asimov_prefitbdt} show the postfits to the data of BDT observable in each SRs with all background processes constrained to the SM expectation.
%The level of discrimination between signal and background achieved by the BDTs is illustrated in Figure~\ref{fig:overtrain_hadhad}-~\ref{fig:overtrain_lhadhad}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\input{\FCNCFigures/tex/BDTinput}
\begin{figure}[H]
\centering
\begin{tabular}{@{}ccc@{}}
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l2tau1bnj_os/tau_pt_0.pdf} &
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b1j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}&
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}\\
\includegraphics[page=1,width=0.33\textwidth]{figures/reg1l2tau1bnj_os.pdf} &
\includegraphics[page=1,width=0.33\textwidth]{figures/reg1l1tau1b1j_ss.pdf}&
\includegraphics[page=1,width=0.33\textwidth]{figures/reg1l1tau1b2j_ss.pdf}\\
(a1) \pT(\tauhad) in $t_l\thadhad$ & (a2) \pT(\tauhad) in  $t_l\tauhad$-1j& (a3) \pT(\tauhad) in $t_l\tauhad$-2j\\
\includegraphics[page=1,width=0.33\textwidth]{figures/reg1l1tau1b2j_os.pdf}&
\includegraphics[page=1,width=0.33\textwidth]{figures/reg1l1tau1b3j_os.pdf}&
\includegraphics[page=1,width=0.33\textwidth]{figures/reg2mtau1b2jos_vetobtagwp70_highmet.pdf}\\
(b1) \pT(\tauhad) in $t_h\tlhad$-2j & (b2) \pT(\tauhad) in  $t_h\tlhad$-3j & (b3) \pT(\tauhad) in $t_h\thadhad$-2j \\
\includegraphics[page=1,width=0.33\textwidth]{figures/reg2mtau1b3jos_vetobtagwp70_highmet.pdf}&\\
(c1) \pT(\tauhad) in $t_h\thadhad$-3j\\
\end{tabular}
\caption{The leading $\thad$ $p_T$  distributions are compared between the expected background and $tuH$ signals in: $t_l\thadhad$ (a1),  $t_l\tauhad$-1j (a2),  $t_l\tauhad$-2j (a3), $t_h\tlhad$-2j (b1), $t_h\tlhad$-3j (b2), $t_h\thadhad$-2j (b3), and $t_h\thadhad$-3j (c1) before the fit to data ('Pre-Fit'). The uncertainty band includes both the statistical and systematic uncertainties in the background prediction. Underflow and overflow bins are included respectively in the first and last bins. Rare including single top, and V+jets and only subtau real refers to t$\bar{t}$ MC with leading tau faked by other object, subleading tau from real contribution. The lower panels show the ratios of the data ('Data') to the background prediction ('Bkg.')}
\label{fig:taupt_prefit}
\end{figure}

% %\input{\FCNCFigures/tex/BDT}
% \begin{figure}[H]
% \centering
% \begin{tabular}{@{}ccc@{}}
% \includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l2tau1bnj_os/BDTG_test.pdf} &
% \includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b1j_ss_vetobtagwp70_highmet/BDTG_test.pdf}&
% \includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_ss_vetobtagwp70_highmet/BDTG_test.pdf}\\
% (a1) BDT dicriminant in $t_l\thadhad$ & (a2) BDT dicriminant in  $t_l\tauhad$-1j& (a3) BDT dicriminant in $t_l\tauhad$-2j\\
% \includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_os_vetobtagwp70_highmet/BDTG_test.pdf} &
% \includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b3j_os_vetobtagwp70_highmet/BDTG_test.pdf} &
% \includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/xTFW/showFake/NOMINAL/reg2mtau1b2jos_vetobtagwp70_highmet/BDTG_test.pdf} \\
% (b1) BDT dicriminant in $t_h\tlhad$-2j & (b2) BDT dicriminant in  $t_h\tlhad$-3j & (b3) BDT dicriminant in $t_h\thadhad$-2j \\
% \includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/xTFW/showFake/NOMINAL/reg2mtau1b3jos_vetobtagwp70_highmet/BDTG_test.pdf} & \\
% (c1) BDT dicriminant in$t_h\thadhad$-3j\\
% \end{tabular}
% \caption{ The BDT output distributions are compared between the expected background and $tqH$ signals in: $t_l\thadhad$ (a1),  $t_l\tauhad$-1j (a2),  $t_l\tauhad$-2j (a3),$t_h\tlhad$-2j (b1), $t_h\tlhad$-3j (b2), $t_h\thadhad$-2j (b3), and $t_h\thadhad$-3j (c1). Only statistical uncertainties are being shown (?). Underflow and overflow bins are included
% respectively in the first and last bins. Empty data bins here are always blinded based on our strategy. The real tau contributions shown from $t\bar{t}$ and other MC including % diboson, single top, and V+jets.}
% \label{fig:asimov_prefitbdt}
% \end{figure}

### 2022-01-19 sections/systematic_uncertainties.tex
solve the commets

>>>>

\begin{table}[htbp]
\caption{List of relative uncertainties of the signal strength from the combined fit in hadronic channel. The uncertainties are symmetrised for presentation and grouped into the categories described in the text. %The quadrature sum of the individual uncertainties is not equal to the total uncertainty due to correlations introduced by the fit
}
\small
\centering
\begin{tabular}{cc} \toprule\toprule
$\text{Uncertainty}    $   & $\Delta\mu/\mu[\%]$ \\\midrule
$\text{Fake modelling} $   & $13.5$ \\
$\text{Instrument}     $   & $2.6$  \\
$\text{Jets}           $   & $1.7$   \\
$\text{Met}            $   & $0.4$   \\
$\tau                  $   & $7.2$    \\
$\text{b-tagging}       $  & $0.3$    \\
$\text{Signal Theory}  $   & $1.5$   \\
$\text{Other MC theory} $  & $2.7$    \\
$t\bar{t} \text{theory}$  & $7.6$     \\\midrule
$\text{Statistics}      $  & $11.2$   \\
$\text{Total systematic}$  & $24.2$  \\ \midrule
$\text{Total}  $           & $26.7$ \\
\bottomrule\bottomrule
\end{tabular}
\label{tab:had_sys_impact}
\end{table}

\begin{table}[htbp]
\caption{List of relative uncertainties of the signal strength from the combined fit in leptonic channel. The uncertainties are symmetrised for presentation and grouped into  the categories described in the text. %The quadrature sum of the individual uncertainties is not equal to the total uncertainty due to correlations introduced by the fit
}
\small
\centering
\begin{tabular}{cc} \toprule\toprule
$\text{Uncertainty}        $ & $  \Delta\mu/\mu[\%]  $\\\midrule
$\text{Fake modelling}     $ & $       2.1             $\\
$\text{Instrument}         $ & $       0.7             $\\
$\text{Jets}               $ & $       2.8             $\\
$\text{Met}                $ & $       1.2             $\\
$\text{Lepton}             $ & $       0.7             $\\
$\tau                      $ & $       2.3             $\\
$\text{b-tagging}          $ & $       4.8             $\\
$\text{Signal Theory}      $ & $       6.9             $\\
$\text{Other MC theory}    $ & $       2.1             $\\
$t\bar{t} \text{theory}    $ & $       3.7             $\\\midrule
$\text{Statistics}         $ & $       5.9             $\\
$\text{Total systematic}   $ & $       12.9            $\\\midrule
$\text{Total}              $ & $       14.2            $\\
\bottomrule\bottomrule
\end{tabular}
\label{tab:had_sys_impact}
\end{table}
